Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-19 paper/paper.tex
Add hyperref package
Title
Clean up figures

\usepackage[pdftex]{graphicx}
% declare the path(s) where your graphic files are
\graphicspath{{./figures/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm,algpseudocode}
\usepackage{url}

@@

% can use linebreaks \\ within to get better formatting as desired
\title{Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds}

% IEE Format
\author{
  \IEEEauthorblockN{Maciej Malawski}
  \IEEEauthorblockA{AGH University of Science and Technology\\
Dept. of Computer Science\\
Krakow, Poland; and\\
University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: mmalawsk@nd.edu}
  \and
  \IEEEauthorblockN{Gideon Juve and Ewa Deelman}
  \IEEEauthorblockA{USC Information Sciences Institute\\
4676 Admiralty Way\\
Marina del Rey, CA, USA\\
Email: \{gideon,deelman\}@isi.edu}
  \and
  \IEEEauthorblockN{Jarek Nabrzyski}
  \IEEEauthorblockA{University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: naber@nd.edu}}

@@

\begin{figure}[htb] 
\centering
\includegraphics[width=1.0\columnwidth]{figures/spds-gantt}
 \caption{Example schedule generated using SPDS algorithm. The colors indicate how various tasks from different workflows are scheduled onto Virtual Machines. }
\label{fig:spds-example}
\end{figure}

@@

\begin{figure}[tb] 
\centering
\includegraphics[width=1.0\columnwidth]{figures/spss-gantt}
 \caption{Example of schedule generated using SPSS algorithm. Tasks are colored by workflow. }
\label{fig:spss-example}
\end{figure}

@@

\begin{figure}[tb] 
\centering
\includegraphics[width=0.6\columnwidth]{figures/ensemble-pareto}
\caption{Pareto-like distribution of workflow sizes in ensemble. Size is
measured in number of tasks.}
\label{fig:ensemble-distribution}
\end{figure}

@@

\begin{figure*}[t] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Number of workflows completed for DPDS, AW-DPDS and SPSS
algorithms on ensembles of 100 Pareto-distributed workflows, {\em small budget}
(top) and {\em large budget} (bottom). The ranges on $y$ axis are chosen to 
emphasize the differences between the performance of the algorithms.}
\label{fig:number-complete-pareto}
\end{figure*}

@@

\begin{figure*}[t]  
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-size-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-size-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-size-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-size-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-size-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{ Total work completed expressed as the sum of runtimes (in hours) of
tasks of completed workflows. Data computed for DPDS, AW-DPDS and SPSS
algorithms on ensembles of 100 Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences between the performance of the algorithms.}
\label{fig:total-time}
\end{figure*}

@@

\begin{figure*}[htb] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Effective computing cost in \$ per hour calculated by dividing the sum of
task runtimes by the total budget. Higher costs result from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences  between  the performance of the algorithms.}
\label{fig:cost}
\end{figure*}

@@

% \begin{figure*}[htb] \centering
% \includegraphics[width=0.19\textwidth]{figures/score2-MONTAGE-n-1000-8-dagh1-20m0.pdf}
% \includegraphics[width=0.19\textwidth]{figures/score2-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
% \includegraphics[width=0.19\textwidth]{figures/score2-LIGO-n-1000-8-dagh1-40m0.pdf}
% \includegraphics[width=0.19\textwidth]{figures/score2-GENOME-n-1000-8-dagh100-1500m0.pdf}
% \includegraphics[width=0.19\textwidth]{figures/score2-SIPHT-n-1000-8-dagh5-50m0.pdf}
% \caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
% Pareto-distributed workflows. Score is computed as $\sum(2^(-p))$ where
% priorities of subsequent workflows are $p=0,1,2,\ldots$ (0 means highest
% priority).} \label{fig:} \end{figure*}

\begin{figure}[htb] \centering
\includegraphics[width=0.7\columnwidth]{figures/pareto-budget-SIPHT-n-1000-8-dagh5-50h4m0.pdf}\\
(a) ensemble of Pareto-distributed workflows
\includegraphics[width=0.7\columnwidth]{figures/constant-budget-SIPHT-n-1000-0-dagh5-50h4m0.pdf}\\
(b) ensemble of workflows of equal size \caption{Comparison of number of
workflows completed for a given deadline, plotted versus different budget
amounts.}
\label{fig:budgets}
\end{figure}

>>>>

\usepackage[pdftex]{graphicx}
\graphicspath{{./figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm,algpseudocode}
\usepackage{hyperref} % must come before url
\usepackage{url}

@@

% can use linebreaks \\ within to get better formatting as desired
\title{Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds}

% IEEE Format
\author{
  \IEEEauthorblockN{Maciej Malawski}
  \IEEEauthorblockA{AGH University of Science and Technology\\
Dept. of Computer Science\\
Krakow, Poland; and\\
University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: mmalawsk@nd.edu}
  \and
  \IEEEauthorblockN{Gideon Juve and Ewa Deelman}
  \IEEEauthorblockA{USC Information Sciences Institute\\
4676 Admiralty Way\\
Marina del Rey, CA, USA\\
Email: \{gideon,deelman\}@isi.edu}
  \and
  \IEEEauthorblockN{Jarek Nabrzyski}
  \IEEEauthorblockA{University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: naber@nd.edu}}

@@

\begin{figure}[htb] 
\centering
\includegraphics[width=1.0\columnwidth]{spds-gantt}
 \caption{Example schedule generated using SPDS algorithm. The colors indicate how various tasks from different workflows are scheduled onto Virtual Machines. }
\label{fig:spds-example}
\end{figure}

@@

\begin{figure}[tb] 
\centering
\includegraphics[width=1.0\columnwidth]{spss-gantt}
 \caption{Example of schedule generated using SPSS algorithm. Tasks are colored by workflow. }
\label{fig:spss-example}
\end{figure}

@@

\begin{figure}[tb] 
\centering
\includegraphics[width=0.6\columnwidth]{ensemble-pareto}
\caption{Pareto-like distribution of workflow sizes in ensemble. Size is
measured in number of tasks.}
\label{fig:ensemble-distribution}
\end{figure}

@@

\begin{figure*}[t] 
\centering
\includegraphics[width=0.19\textwidth]{pareto-MONTAGE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-CYBERSHAKE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-LIGO-n-1000-8-dagh1-40m0}
\includegraphics[width=0.19\textwidth]{pareto-GENOME-n-1000-8-dagh100-1500m0}
\includegraphics[width=0.19\textwidth]{pareto-SIPHT-n-1000-8-dagh5-50m0}
\caption{Number of workflows completed for DPDS, AW-DPDS and SPSS
algorithms on ensembles of 100 Pareto-distributed workflows, {\em small budget}
(top) and {\em large budget} (bottom). The ranges on $y$ axis are chosen to 
emphasize the differences between the performance of the algorithms.}
\label{fig:number-complete-pareto}
\end{figure*}

@@

\begin{figure*}[t]  
\centering
\includegraphics[width=0.19\textwidth]{pareto-size-MONTAGE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-size-CYBERSHAKE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-size-LIGO-n-1000-8-dagh1-40m0}
\includegraphics[width=0.19\textwidth]{pareto-size-GENOME-n-1000-8-dagh100-1500m0}
\includegraphics[width=0.19\textwidth]{pareto-size-SIPHT-n-1000-8-dagh5-50m0}
\caption{ Total work completed expressed as the sum of runtimes (in hours) of
tasks of completed workflows. Data computed for DPDS, AW-DPDS and SPSS
algorithms on ensembles of 100 Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences between the performance of the algorithms.}
\label{fig:total-time}
\end{figure*}

@@

\begin{figure*}[htb] 
\centering
\includegraphics[width=0.19\textwidth]{pareto-cost-MONTAGE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-LIGO-n-1000-8-dagh1-40m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-GENOME-n-1000-8-dagh100-1500m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-SIPHT-n-1000-8-dagh5-50m0}
\caption{Effective computing cost in \$ per hour calculated by dividing the sum of
task runtimes by the total budget. Higher costs result from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences  between  the performance of the algorithms.}
\label{fig:cost}
\end{figure*}

@@

% \begin{figure*}[htb] \centering
% \includegraphics[width=0.19\textwidth]{score2-MONTAGE-n-1000-8-dagh1-20m0}
% \includegraphics[width=0.19\textwidth]{score2-CYBERSHAKE-n-1000-8-dagh1-20m0}
% \includegraphics[width=0.19\textwidth]{score2-LIGO-n-1000-8-dagh1-40m0}
% \includegraphics[width=0.19\textwidth]{score2-GENOME-n-1000-8-dagh100-1500m0}
% \includegraphics[width=0.19\textwidth]{score2-SIPHT-n-1000-8-dagh5-50m0}
% \caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
% Pareto-distributed workflows. Score is computed as $\sum(2^(-p))$ where
% priorities of subsequent workflows are $p=0,1,2,\ldots$ (0 means highest
% priority).} \label{fig:} \end{figure*}

\begin{figure}[htb] \centering
\includegraphics[width=0.7\columnwidth]{pareto-budget-SIPHT-n-1000-8-dagh5-50h4m0}\\
(a) ensemble of Pareto-distributed workflows
\includegraphics[width=0.7\columnwidth]{constant-budget-SIPHT-n-1000-0-dagh5-50h4m0}\\
(b) ensemble of workflows of equal size \caption{Comparison of number of
workflows completed for a given deadline, plotted versus different budget
amounts.}
\label{fig:budgets}
\end{figure}
